\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2023-03-09 R/comparison_table.Rmd
Fixing output_file for 10.comparison_table.md

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '11.comparison_table.md'))})
output: 
  md_document:
    variant: gfm #forces table to be markdown, not html
---

>>>>

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '10.comparison_table.md'))})
output: 
  md_document:
    variant: gfm #forces table to be markdown, not html
---
